Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2018-10-15 pkg/disttree/inst/draft/rejoinder.tex
some more revision based on reviews and feedback
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2326 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 0f09150666914e1d76d6048a151708759a87441a

\documentclass[american,foldmarks=false,noconfig]{uibklttr}
%\documentclass{article}
\usepackage{sfmath,hyperref,color,enumitem,soul}

@@

\item The more extensive evaluations for station Axams have been 
carried out for 14 other observation stations. Results are 
provided in an online supplement which comes with our revised manuscript.

\item The evaluations performed for all 95 observation stations 
have been carried out under different distribution assumptions 
for the response variable in order to test for robustness against
distributional misspecifications. Results are provided in an 
online supplement.

@@

@@

The required size of the training data depends heavily on the complexity 
of the model, however, in different applications which we have tested the 
distributional forest on it performed quite well with at least 50 observations. \\
Applying the Law of Large Numbers it can be shown that random forests do not overfit, 
not even for an increasing number of trees (Breiman (2001), Hastie et al. (2001), 
Biau et al. (2016)). Therefore, it is recommended to build a large number of trees
as this generally leads to more accurate predictions. However, ``the computational cost 
for inducing a forest increases linearly with the number of trees, so a good choice 
results from a trade-off between computational complexity and accuracy'' 
(Biau et al. (2016)). Following this advice, we decided to build forests consisting 
of 100 trees.\\
Moreover, Hastie et al. (2001) recommend to build trees of maximal depth:
``Our experience is that using full-grown trees seldom costs much, and 
results in one less tuning parameter.''
Thus, the stopping criteria \texttt{minbucket} and \texttt{minsplit} (both 
determining the minimal number of observations in a node) and \texttt{alpha} 
(the significance level for the statistical tests in the tree algorithm) should 
be kept rather low. However, in a distributional framework it also has to be 
considered that the minimal number of observations in a node needs to be high 
enough in order to allow for estimating the distribution parameters reasonably well.
In our application we have set \texttt{minsplit} to 50 and \texttt{minbucket} to 20.
These tuning parameters are now also listed in the main manuscript in Sections~3.2.
and discussed in Section~4..

@@

We have measured fitting time and prediction time in our 
application. For single predictions the distributional forest 
can keep up with the other models. However, as you already 
stated correctly, each prediction made by the forest is based 
on an observation-specific weight matrix and therefore has to 
be calculated separately. For that reason prediction time for a 
set of observations is clearly higher for the forest model than 
the GAMLSS models or the EMOS. The exact results and times can 
be found in an online supplement.

@@

We have rephrased this as 'expert knowledge in the application domain'
in Section~2.2..

@@

Axams was chosen as the observation station being closest 
to Innsbruck, the capital of Tyrol and the work place of 
three of the authors, but not based on any other particular 
features. Furthermore, it has been checked, whether it 
is an adequate representative of all stations regarding 
the results of our evaluations. This is now also 
confirmed by further analysis in the online supplement which
comes along with our manuscript and discussed in Section~4..

@@

East Tyrol is located south of the main Alpine Ridge and exhibits different
climatological characteristics than the part north of the Alpine Ridge.  It
seems that the choice of covariates and their interactions we made for the
prespecified GAMLSS method is particularly adequate for the region of East
Tyrol for this specific analysis. However, the advantages of the prespecified
GAMLSS models in this particular setting (training: 1985--2008, validation:
2009--2012) even out in a cross-validation framework for most of the stations
in East Tyrol. These results are presented in the online supplement which comes
along with our manuscript showing that the forest performs equally well as the
prespecified GAMLSS and better than the EMOS at most of the stations.
Moreover, this point is now also discussed in Section~4. in the main manuscript.

@@

We have rephrased this part of the caption to 'Observations are non-negative 
and modeled by a Gaussian distribution, left-censored at 0.
The observations are depicted by crosses and the predicted point mass
from the model by filled circles.' to clearly distinguish between the model
and the observations.

@@

We have rephrased this the second paragraph of Section~2.3. which
included this sentence.

@@

Yes, in the forest model the parameter vector has to be estimated 
separately for each new prediction as it is based on an 
observation-specific weight matrix. For that reason, making 
predictions for a set of new observations is clearly more 
time consuming for the forest model than the GAMLSS models 
or the EMOS model. However, the time needed to make one single 
prediction is similar for all methods. The exact results 
concerning fitting and prediction times can be found in an online 
supplement.

@@

As stopping criteria the minimal number of observations to perform 
a split (\texttt{minsplit}) is set to 50,  the minimal number of 
observations in a terminal node (\texttt{minbucket}) is set to 20 
and the significance level for variable selection (\texttt{alpha}) 
is kept at the default value 1. We have added this information in 
the manuscript in Section~3.2., 'Distributional forest' and
also discussed the choice of these values in Section~4. and
in the answer to the second point of the associate editor.

@@

Figure 6 shows the variable importance of the distributional forest
for one specific case (similar for other sites and cross-folds) 
using a CRPS based variable importance measure. The subset of 
most important covariates is similar to the set of covariates 
used for the prespecified GAMLSS but not equivalent.
The use of different variations of the same covariate (cf., Table 2)
is not surprising as the covariates are often highly correlated.
Compared to the prespecified GAMLSS the forest seems to depict some
features via differences among the different variations of a specific
covariate (e.g., use \code{tp\_max}, \code{tp\_mean}, and \code{tp\_min}).
Unfortunately the analysis does not allow to get more insights
of (the importance of) interactions between different covariates.

\begin{reto}
Oder sowas \dots Oder g\"abe es daf\"ur tests in W\"aldern?
\end{reto}

@@

Apologies for the unclear notation in Appendix A. This has been 
revised in the manuscript, also regarding your comments 17--20,
and we hope that it now clarifies the content.

Depending on whether the split variable $Z_l$ is a numeric 
or a categorical variable, $t_l$ is either a
$k$~-~or~$k \cdot H$~-~dimensional vector.

@@

Apologies again for the confusing notation. Here we are 
actually referring to the linear statistic $t_l$ (instead of $t$) 
which is the observed value of $T_l$, the test statistic for 
the $l$-th split variable $Z_l$.

@@

As in the foregoing point this was just a general notation, but 
actually the variables corresponding to the $l$-th split variable 
are considered, i.e. $t_l$, $\mu_l$ and $\sigma_l$. Thank you for
pointing this out, now the missing indices are set.

@@

Again, we are sorry for a confusing explanation. The two subgroups 
are not ordered which is also not necessary as only the sum of 
scores over the two subgroups is considered for the linear 
statistic $T_{l^{\ast}}^{qr}$.

@@

We have applied the left-censored at zero Gaussian distribution
as it has proven to be an adequate choice for this type of 
application in earlier publications.
Moreover, the residual QQ plots and PIT histograms illustrate
that the models are well calibrated employing this distribution.
But thank you very much for the advice to consider a hurdle model!
This is definitely a good idea and therefore we have carried out the
same evaluations as presented in the paper but employing a
Gaussian hurdle model. Additionally, a left-censored at zero logistic
distribution has been applied as well in the same setting in
order to account for heavier tails. The results of these evaluation
can be found in the online supplement 1 (``Different Response Distributions''). 
Overall, it is shown that under the logistic distribution the methods perform 
slightly worse while the hurdle model leads to small improvement in some settings,
however, this comes along with broader variability. The distributional 
forest is proven to be very robust against distributional misspecifications.
Based on these results we decided to keep the distributional assumption
considered in the main manuscript but we have also discussed the tested
alternatives in Section~4..

@@

Thank you for your suggestions and the references. These are all
good ideas, however, in our application the number of covariates
is too large in order to keep a model with all interactions manageable.
We have also discussed this in Section~4 of the main manuscript and
rephrased the corresponding sentence in the introduction to ``while 
requiring no meteorological knowledge about the atmospheric processes 
which drive formation of precipitation'' in order to clarify that
this refers only to the variable prespecification in this application.

@@

In order to investigate on these questions we have carried out the full
analysis as presented for station Axams in the main manuscript for 14
further observation stations. It shows that the distributional
forest is very robust against distributional misspecifications
and almost always competitive with the best among the other methods 
or even better. The exact results are provided in 
Supplement 2 (Stationwise Evaluation) and discussed in Section~4. 
Especially for meteorologists intending to apply model output 
statistics (MOS) for several hundreds of observation stations 
(\hl{\texttt{FIXME: reference Reto}})
the distributional forest provides a good and robust alternative. 
Even though computational costs are higher than for an EMOS model, 
they are similar as for a prespecified model and lower than for 
a model applying variable selection based on cross-validation.

@@

The folds of the cross-validation are chosen randomly. The data 
set of 28 years is split randomly into 7 blocks of 4 years which 
are not necessarily successive. This is now also explained in the 
description of the cross-validation setup third paragraph of 
Section~3.3..
We have chosen two different setups: First we learned the model
on the first 24 years and evaluated on the following 4 years
in order to provide a classic time ordered setup. 
However, following (\hl{\texttt{FIXME:} reference Reto})
no influence of time is to be expected. This is also supported by an 
autocorrelation coefficient of -0.007 of the out-of-bag quantile 
residuals of the distributional forest model for station Axams for
a time lag of 1 day.
% ## calculation of autocorrelation:
% load("Axams_24to4.rda") 
% set.seed(4)
% pdf <- predict(Axams_24to4$df, newdata = Axams_24to4$testdata, type = "parameter")
% pit_df <- cbind(0, pnorm(Axams_24to4$testdata[,"robs"], mean = pdf$mu, sd = pdf$sigma))
% pit_df[Axams_24to4$testdata[,"robs"]>0, 1] <- pit_df[Axams_24to4$testdata[,"robs"]>0, 2]
% ac <- acf(qqrplot(pit_df)$residuals)
Then, to evaluate the models in a broader framework a cross-validation 
with the above described choice of folds was applied, for station
Axams in the main manuscript and for 14 further stations in 
Supplement 2 (Stationwise Evaluation).

@@

As mentioned in point 5 and also discussed in Section~4, the high
number of covariates (80) restricts the possibilities of variable selection
and specification. For an AIC or BIC based selection an evaluation
of 80 main effects for two parameters would make this a very complex
procedure. Moreover, Hofner et al. (2016) stated that the 
AIC-based variable selection methods implemented in the \textsf{R} 
package \textbf{gamlss} ``can be unstable, especially when it comes 
to selecting possibly different sets of variables for 
multiple distribution parameters.'' For that reason we decided
not to choose such a selection method.

@@

By a `basic EMOS' we are referring to the linear distributional 
regression model based on the idea presented by Gneiting et al. (2005) 
applying a left-censored at zero Gaussian distribution where only the 
ensemble mean is included for the location parameter and the ensemble 
standard deviation for the scale parameter.
We have introduced the model which we are referring to as a basic EMOS 
in detail in the main manuscript in the first paragraph of Section~3.

@@

As now discussed in Section~4 including only all pairwise interactions
of the 80 available variables would already lead to 3160 additional
covariates which would make the model too complex and hardly manageable
regarding computational costs. Therefore, we decided not to include
any interactions in the boosting algorithm.
% factorial(80)/factorial(80-2)/factorial(2)

@@

Following Breiman (2001) random forests are very robust and do not overfit, 
not even for a high number of trees. However, computational costs increase 
linearly with the number of trees (Biau et al. (2016)).
Therefore, we followed these recommendations of choosing a high number of
trees, but still not too high in order to keep the computation time at
a reasonable level. Moreover, 100 is a commonly used number of trees that
seems to work very well. Of course, more trees could be applied but 
the performance is usually not significantly worse with 100 trees.
Tuning parameters of forest models, including the number of 
trees (\texttt{ntree}), are now discussed in Section~4 
of the main manuscript.

@@

We used ``EMOS'' as an expression for a standard post-processing
model output statistics (MOS, Gneiting et al. (2005)) with a censored 
distribution. We have revised the introduction of the EMOS model in 
the main manuscript in Section~3 and hope this now explains the model better.

\textit{FIX ME: refer to better explanation in the paper}

@@

The PIT histograms and the residual QQ plots visualize the same
results on different scales. The out-of-sample PIT values are 
either plotted in a histogram or plotted against the corresponding
quantiles of the standard normal distribution. A more detailed 
explanation can be found in Supplement 2 (Stationwise Evaluation) 
which contains both, PIT histograms and residual QQ plots, 
for 15 stations. In the manuscript we decided to show only the 
residual QQ plot as it allows for a better analysis of tail 
behavior than the PIT histogram.

@@

Figure 6 shows the 10 most important covariates of the forest model
in one particular setting (station Axams, learned on 1985--2008). 
Variable importance has been calculated for all covariates, however,
we decided to present only the top 10 as all following covariates 
are on a rather low and similar level not providing further useful
information. But this top 10 list is not considered for any 
specification of the boosted GAMLSS for which all available 
covariates are included. As for the distributional forest, 
we have also calculated variable importance based on mean increase 
of out-of-bag CRPS for the gamboostLSS model for the exact same 
setting (station Axams, learned on 1985--2008). The resulting 
top 10 variables are listed in the following barplot:

\begin{center}
\includegraphics[width = 0.4\textwidth]{varimp_gb.jpeg}
\end{center}

Overall it can be stated that the most important covariates of the boosted 
GAMLSS are similar to the ones of the distributional forest even though they
are not exactly the same ones and the influence of \texttt{tp\_max} is clearly
stronger in the boosted GAMLSS.

@@

@@

\item[] Chen, J., Brissette, F. P. and Lhi, Z. (2014). Postprocessing 
of ensemble weather forecasts using a stochastic weather generator, 
\textit{Monthly Weather Review}.

\item[] Goicoa, T., Adin, A., Ugarte, M. D. and Hodges, J. S. (2017). 
In spatio-temporal disease mapping models, identifiability constraints 
affet PQL and INLA results, \textit{Stochastic Environmental Research 
and Risk Assessment} p. to appear.

\item[] Ugarte, M. D., Adin, A. and Goicoa, T. (2017). One-dimensional, 
two-dimensional, and three-dimensional B-splines to specify space-time 
interactions in bayesian disease mapping: Model fitting and model 
identifiability, \textit{Spatial Statistics} p. to appear.

\item[] Wood, S. N., Scheipl, F. and Faraway, J. J. (2013). 
Straightforward intermediate rank tensor product smoothing in mixed models, 
\textit{Statistics and Computing} \textbf{23}: 341--360.

@@

\item[] Hofner, B., Boccuto, L. and Goeker, M. (2015). 
Controlling false discoveries in high-dimensional situations: Boosting 
with stability selection,
\textit{BMC Bioinformatics} \textbf{16:144}.

@@

\item[] Hastie, T., Tibshirani, R. and Friedman, J. (2001).
The Elements of Statistical Learning,
\textit{Springer New York Inc.}.

@@

>>>>

\documentclass[american,foldmarks=false,noconfig]{uibklttr}
%\documentclass{article}
\usepackage{sfmath,hyperref,color,enumitem,soul}
%% additional style file to include bibliograph in class uibklttr
%\usepackage{letterbib}
%\usepackage{natbib,hyperref}

@@

\item The evaluations performed for all 95 observation stations 
in the main manuscript have been carried out under different 
distribution assumptions for 15 observation stations in order to 
test for robustness against distributional misspecifications. 
Results are provided in an online supplement 
(Supplement 1: Different Response Distributions) 
which comes with our revised manuscript.

\item The more extensive evaluations for station Axams have been 
carried out for 14 other observation stations. Results are 
provided in an online supplement 
(Supplement 2: Stationwise Evaluation)
which comes with our revised manuscript.

@@

\item In the calculation of variable importance we have detected some inconsistencies.
Thus, we have revised the applied method to evaluate this measurement and recalculated
variable importance for the distributional forest.

@@

The required size of the training data heavily depends on the complexity 
of the model, however, in different applications where we have tested the 
distributional forest it performed quite well with at least 50 observations. \\
Applying the Law of Large Numbers it can be shown that random forests do not overfit, 
not even for an increasing number of trees (Breiman 2001, Hastie et al. 2001, 
Biau et al. 2016). Therefore, it is recommended to build forests with a large number 
of trees as this generally yields more accurate predictions. 
However, ``[\dots] the computational cost for inducing a forest increases linearly 
with the number of trees, so a good choice results from a trade-off between 
computational complexity and accuracy'' (Biau et al. 2016, p.~205). Following this 
advice, we decided to build forests consisting of 100 trees.\\
Moreover, Hastie et al. (2001, p.~596) recommend to build trees of maximal depth:
``Our experience is that using full-grown trees seldom costs much, and 
results in one less tuning parameter.''
Thus, the stopping criteria \texttt{minbucket} and \texttt{minsplit} (both 
determining the minimal number of observations in a node) and \texttt{alpha} 
(the significance level for the statistical tests in the tree algorithm) should 
be kept rather low. However, in a distributional framework it also has to be 
considered that the minimal number of observations in a node needs to be high 
enough in order to allow for estimating the distribution parameters reasonably well.
In our application we have set \texttt{minsplit} to 50 and \texttt{minbucket} to 20.
These tuning parameters are now also listed in the main manuscript in Sections~3.2.
and discussed in Section~4.

@@

We have measured fitting time and prediction time for our 
application. For single predictions the distributional forest 
can keep up with the other models. However, as you already 
stated correctly, each prediction made by the forest is based 
on an observation-specific weight matrix and therefore has to 
be calculated separately. For that reason prediction time for a 
set of observations is clearly higher for the forest model than 
the GAMLSS models or the EMOS. The exact results and times can 
be found in Supplement 2 (Stationwise Evaluation).

@@

We have rephrased this as 'expert knowledge in the application domain'
in Section~2.2.

@@

Axams was chosen as the observation station being closest 
to Innsbruck, the capital of Tyrol and the work place of 
three of the authors, but not based on any other particular 
features. Furthermore, it has been checked whether it 
is an adequate representative of all stations regarding 
the results of our evaluations. This is now also 
confirmed by further analysis in Supplement 2 (Stationwise Evaluation) 
and discussed in Section~4.

@@

This seems to result from the one specific training and validation period 
(training: 1985--2008, validation: 2009-2012).
The advantages of the GAMLSS model even out at most of the stations when looking 
on the results of a cross-validation. We have extended Section~4 to discuss this 
issue. The results of a the extended cross-validation for a set of $15$ stations 
can be found in Supplement 2 (Stationwise Evaluation).

@@

We have rephrased this part of the caption to ``Observations are non-negative 
and modeled by a Gaussian distribution, left-censored at 0.
The observations are depicted by crosses and the predicted point mass
from the model by filled circles.'' to clearly distinguish between the model
and the observations.

@@

We have rephrased the second paragraph of Section~2.3.

@@

Yes, in the forest model the parameter vector has to be estimated 
separately for each new prediction as it is based on an 
observation-specific weight matrix. For that reason, making 
predictions for a set of new observations is clearly more 
time consuming for the forest model than the GAMLSS models 
or the EMOS model. However, the time needed to make one single 
prediction is similar for all methods. The exact results 
concerning fitting and prediction times can now be found in
Supplement 2 (Stationwise Evaluation).

@@

As stopping criteria the minimal number of observations to perform 
a split (\texttt{minsplit}) is set to 50, the minimal number of 
observations in a terminal node (\texttt{minbucket}) is set to 20 
and the significance level for variable selection (\texttt{alpha}) 
is kept at the default value 1. We have added this information in 
the manuscript in Section~3.2., 'Distributional forest' and
also discussed the choice of these tuning parameter in Section~4. and
in the answer to the second point of the associate editor.

@@

Figure 6 shows the variable importance of the distributional forest
for one specific case (similar for other sites and cross-folds) 
using a CRPS based variable importance measure. The subset of 
most important covariates is similar to the set of covariates 
used for the prespecified GAMLSS but not equivalent.
The selection of different variations of the same covariate (cf., Table 2)
is not surprising as the covariates are often highly correlated.
Moreover, in the distributional forest for each node only a randomly
drawn subset of covariates is considered. Hence, if for example the most 
influential covariate is not included in this subset for a specific node 
a similar covariate is very likely to be selected instead.
Compared to the prespecified GAMLSS the forest seems to depict some
features via differences among the different variations of a specific
covariate (e.g., use \code{tp\_max}, \code{tp\_mean}, and \code{tp\_min}).
Unfortunately the analysis does not allow to get more insights
of (the importance of) interactions between different covariates.

@@

Apologies for the unclear notation in Appendix A.
Depending on whether the split variable $Z_l$ is a numeric 
or a categorical variable, $t_l$ is either a
$k$~-~or~$k \cdot H$~-~dimensional vector.
We have revised the corresponding parts in the manuscript (also 
regarding your comments 17--20) and we hope that it now clarifies 
the content.

@@

Here we are actually referring to the linear statistic $t_l$ (instead of $t$) 
which is the observed value of $T_l$, the test statistic for the $l$-th split 
variable $Z_l$. This has been adjusted in the Appendix of the manuscript.

@@

As in the foregoing point this was just a general notation, but 
actually the variables corresponding to the $l$-th split variable 
are considered, i.e. $t_l$, $\mu_l$ and $\sigma_l$. Thank you for
pointing this out, the missing indices have been added in the
Appendix of the manuscript.

@@

The two subgroups are not ordered which is also not necessary as only 
the sum of scores over the two subgroups is considered for the linear 
statistic $T_{l^{\ast}}^{qr}$. We have adjusted the Appendix of
the manuscript to clarify this issue.

@@

We have applied the left-censored at zero Gaussian distribution
as it has proven to be an adequate choice for this type of 
application in earlier publications.
Moreover, the residual QQ plots and PIT histograms illustrate
that the models are well calibrated employing this distribution.
But thank you very much for the advice to consider a hurdle model!
This is definitely a good idea and therefore we have carried out the
same evaluations as presented in the paper but employing a
Gaussian hurdle model. Additionally, a left-censored at zero logistic
distribution has been applied as well in the same setting in
order to account for heavier tails. The results of these evaluation
can be found in Supplement 1 (Different Response Distributions). 
Overall, the distributional forest is proven to be very robust against 
distributional misspecifications. Therefore, we decided to keep the 
distributional assumption considered in the main manuscript but we have 
also discussed the tested alternatives in Section~4.

@@

Thank you for your suggestions and the references. These are all
good ideas, however, in our application the number of covariates
is too large in order to keep a model with all interactions manageable.
We have also discussed this in Section~4 of the main manuscript and
rephrased the corresponding sentence in the introduction to ``while 
requiring no meteorological knowledge about the atmospheric processes 
which drive formation of precipitation for the model specification.'' 
in order to clarify that this refers only to the variable prespecification 
in this application.

@@

In order to investigate on these questions we have carried out the full
analysis as presented for station Axams in the main manuscript for 14
further observation stations. It shows that the distributional
forest is very robust against distributional misspecifications
and almost always competitive with the best among the other methods 
or even better. The exact results are provided in 
Supplement 2 (Stationwise Evaluation) and discussed in Section~4. 
Especially for meteorologists intending to apply model output 
statistics (MOS) for several hundreds of observation stations 
(e.g., Wahl 2014, Rasp and Lerch 2018)
the distributional forest provides a good and robust alternative. 
Even though computational costs are higher than for an EMOS model, 
they are similar as for a prespecified model and lower than for 
a model applying variable selection based on cross-validation.
Execution times have been measured and can be found
in Supplement~2 (Stationwise Evaluation).

@@

The folds of the cross-validation are chosen randomly. The data 
set of 28 years is split randomly into 7 blocks of 4 years which 
are not necessarily successive. This is now also explained in the 
description of the cross-validation setup third paragraph of 
Section~3.3.

We have chosen two different setups: First we learned the model
on the first 24 years and evaluated on the following 4 years
in order to provide a classic time ordered setup. 
However, no influence of time is to be expected which is also supported by 
an autocorrelation coefficient of -0.007 of the out-of-bag quantile 
residuals of the distributional forest model for station Axams for
a time lag of 1 day.
% ## calculation of autocorrelation:
% load("Axams_24to4.rda") 
% set.seed(4)
% pdf <- predict(Axams_24to4$df, newdata = Axams_24to4$testdata, type = "parameter")
% pit_df <- cbind(0, pnorm(Axams_24to4$testdata[,"robs"], mean = pdf$mu, sd = pdf$sigma))
% pit_df[Axams_24to4$testdata[,"robs"]>0, 1] <- pit_df[Axams_24to4$testdata[,"robs"]>0, 2]
% ac <- acf(qqrplot(pit_df)$residuals)
To evaluate the models in a broader framework a cross-validation 
with the above described choice of folds was applied. The results
for station Axams are included in the main manuscript, results
for 14 additional stations can be found in
Supplement~2 (Stationwise Evaluation).

@@

As mentioned in our response to your comment 5, and also discussed in Section~4, 
the high number of covariates (80) restricts the possibilities of variable 
selection and model specification. For an AIC or BIC based selection an 
evaluation of 80 main effects for two parameters would make this a very complex
procedure. Moreover, Hofner et al. (2016, p.~3) stated that the 
AIC-based variable selection methods implemented in the \textsf{R} 
package \textbf{gamlss} ``[...] can be unstable, especially when it comes 
to selecting possibly different sets of variables for 
multiple distribution parameters.'' For that reason we decided
not to apply such a selection method.

@@

By a `basic EMOS' we are referring to the linear distributional 
regression model based on the idea presented by Gneiting et al. (2005) 
applying a left-censored at zero Gaussian distribution where only the 
ensemble mean is included for the location parameter and the ensemble 
standard deviation for the scale parameter.
We now introduce the model which we are referring to as a `basic EMOS'
in detail in the main manuscript in the first paragraph of Section~3.

@@

Including only pairwise interactions
of the 80 available variables would already lead to 3160 additional
covariates which would make the model too complex and hardly manageable
regarding computational costs. Therefore, we decided not to include
any interactions in the boosting algorithm.
This issue is now addressed and discussed in Section~4.
% factorial(80)/factorial(80-2)/factorial(2)

@@

Following Breiman (2001) random forests are very robust and do not overfit, 
not even for a high number of trees. However, computational costs increase 
linearly with the number of trees (Biau et al. 2016).
Therefore, we followed these recommendations of choosing a high number of
trees, but still small enough to keep the computation time at
a reasonable level. Moreover, 100 is a commonly used number of trees that
seems to work very well. A larger number of trees could be used but 
the performance is usually not significantly better compared to a forest with 
100 trees. Tuning parameters of forest models, including the number of 
trees (\texttt{ntree}), are now discussed in Section~4 
of the main manuscript.

@@

The EMOS as originally suggested by Gneiting et al. (2005) can be seen
as one of the standard ensemble model output statistics (or post-processing)
approaches. This concept is well known within the post-processing community.
We have revised the introduction of our manuscript and introduce the `basic EMOS'
in more explicitly and in more detail (cf., Section~3).

@@

The PIT histograms and the residual QQ plots visualize the same
results on different scales. The out-of-sample PIT values are 
either plotted in a histogram or plotted against the corresponding
quantiles of the standard normal distribution. A more detailed 
explanation can be found in Supplement 2 (Stationwise Evaluation) 
which contains both, PIT histograms and residual QQ plots, 
for 15 stations. In the manuscript we decided to only show the 
residual QQ plot as it allows for a better analysis of the tail 
behavior than the PIT histogram.

@@

Figure 6 is only a visualization of the 10 most important covariates 
of the forest model in one particular setting (station Axams, learned 
on 1985--2008). However, this top 10 list is not considered for any specification 
of the boosted GAMLSS for which all available covariates are included. As 
for the distributional forest, we have also calculated variable importance 
based on mean increase of out-of-bag CRPS for the gamboostLSS model for 
the exact same setting (station Axams, learned on 1985--2008). The resulting 
top 10 variables are listed in the following barplot.

\begin{center}
\includegraphics[width = 0.7\textwidth]{varimp_gb.jpeg}
\end{center}

Overall it can be stated that the most important covariates of the boosted 
GAMLSS are similar to the ones of the distributional forest even though they
are not exactly the same ones and the influence of \texttt{tp\_max} is clearly
stronger in the boosted GAMLSS. This can be explained by the random selection
of possible split variables in each node of the distributional forest. Thus,
if \texttt{tp\_max} is not available, a similar covariate such as \texttt{tp\_min}
or \texttt{tp\_mean} are very likely to be selected instead while in the boosting
algorithm \texttt{tp\_max} is always a possible choice.

@@

%\bibliographystyle{jss}
%\bibliography{ref.bib}

@@

\item[] Chen, J., Brissette, F. P. and Lhi, Z. (2014). Postprocessing 
of Ensemble Weather Forecasts Using a Stochastic Weather Generator, 
\textit{Monthly Weather Review}.

%\item[] Goicoa, T., Adin, A., Ugarte, M. D. and Hodges, J. S. (2017). 
%In Spatio-Temporal Disease Mapping Models, Identifiability Constraints 
%Affet PQL and INLA Results, \textit{Stochastic Environmental Research 
%and Risk Assessment} p. to appear.

%\item[] Ugarte, M. D., Adin, A. and Goicoa, T. (2017). One-Dimensional, 
%Two-Dimensional, and Three-Dimensional B-Splines to Specify Space-Time 
%Interactions in Bayesian Disease Mapping: Model Fitting and Model 
%Identifiability, \textit{Spatial Statistics} p. to appear.

\item[] Goicoa, T., Adin, A., Ugarte, M. D. and Hodges, J. S. (2018). 
In Spatio-Temporal Disease Mapping Models, Identifiability Constraints 
Affet PQL and INLA Results, \textit{Stochastic Environmental Research 
and Risk Assessment} \textbf{32, 3}: 749--770.

\item[] Ugarte, M. D., Adin, A. and Goicoa, T. (2017). One-Dimensional, 
Two-Dimensional, and Three-Dimensional B-Splines to Specify Space-Time 
Interactions in Bayesian Disease Mapping: Model Fitting and Model 
Identifiability, \textit{Spatial Statistics} \textbf{22}: 451--468.

\item[] Wood, S. N., Scheipl, F. and Faraway, J. J. (2013). 
Straightforward Intermediate Rank Tensor Product Smoothing in Mixed Models, 
\textit{Statistics and Computing} \textbf{23}: 341--360.

@@

%\item[] Hofner, B., Boccuto, L. and Goeker, M. (2015). 
%Controlling false discoveries in high-dimensional situations: Boosting 
%with stability selection,
%\textit{BMC Bioinformatics} \textbf{16:144}.

@@

\item[] Hastie, T., Tibshirani, R. and Friedman, J. (2001).
The Elements of Statistical Learning, Second Edition,
\textit{Springer New York Inc.}.

@@

\item[] Wahl, S. (2015). Uncertainty in Mesoscale Numerical Weather Prediction:
Probabilistic Forecasting of Precipitation, PhD thesis, 
\textit{University of Bonn}, p. 1--120.% \url{http://hss.ulb.uni-bonn.de/2015/4190/4190.pdf}.

\item[] Rasp, S., Lerch, S. (2018). Neural Networks for Post-Processing Ensemble
Weather Forecasts, \textit{Montly Weather Review}, NA.
%doi:\href{https://doi.org/10.1175/MWR-D-18-0187.1}{10.1175/MWR-D-18-0187.1}.
